The Name of the Title is Hope

### 2020-03-18 paper.tex
More stuff

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

@@

>>>>

\author{Michael James}
\affiliation{%
  \institution{University of California, San Diego}
}
\email{m3james@eng.ucsd.edu}

\author{John Renner }
\affiliation{%
  \institution{University of California, San Diego}
}
\email{jmrenner@eng.ucsd.edu}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
    Abstracts are scary.
\end{abstract}

@@

\section{Method}
% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
% Explain your study design, illustrate how the study's results will provide
% evidence for/against your hypothesis, and how the question, hypothesis, and
% study all line up. We encourage you to mirror/copy/adapt other researchers
% methods (e.g. by drawing from the class readings) whenever appropriate (and
% not when it isn't appropriate).

% There are three major points you should hit here.

% Study design:
% What are you going to do? Be detailed and precise.

% Measures:
% How will you know you succeeded? What will you measure? How will you measure
% it? What might your results look like?

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{results/task_points.png}
  \caption{
    Examples did not noticeably affect time-to-completion, except in Task 2
    where the effect is dramatic.
  }
  \label{fig:data-points}
\end{figure*}

\section{Results}
% Figures.
% Analysis
\section{Discussion}
